Bayesian non-parametric inference for multivariate peaks-over-threshold models

### 2024-04-10 abstract.tex
entropy submission RC1
push for mdpi resubmission

We consider a constructive definition of the multivariate Pareto that factorizes the 
random vector into a radial component and an independent angular component; The former
following a univariate Pareto distribution, and the latter defined on the surface of the 
positive orthant of the infinity norm unit hypercube.  In this paper, we  propose a method 
for inferring the distribution of the angular component.  We identify its support 
as the limit of the positive orthant of the unit $p$--norm spheres, and introduce a 
projected gamma family of distributions defined through the normalization a vector of 
independent gamma random variables to the $p$--norm sphere.  This family serves as a 
building block for a flexible family of distributions obtained as a Dirichlet process 
mixture of projected gammas.  For model assessment, we discuss scoring methods appropriate 
to distributions on the unit hypercube.  In particular, working with the energy score
criterion, we develop a kernel metric that produces a  proper scoring rule, and present 
a simulation study to compare  different modeling choices using the proposed scoring rules.  
Finally we apply our  approach to describe the dependence structure of the extreme values of 
the magnitude  of the integrated vapor transport (IVT), data describing the flow 
of atmospheric moisture along the coast of California for the years of 1979 
through 2020.  We find clear but heterogeneous geographical dependence.

% EOF

>>>>

We consider a constructive definition of the multivariate Pareto that factorizes the 
random vector into a radial component and an independent angular component; The former
following a univariate Pareto distribution, and the latter defined on the surface of the 
positive orthant of the infinity norm unit hypercube.  In this paper, we  propose a method 
for inferring the distribution of the angular component.  We identify its support 
as the limit of the positive orthant of the unit $p$-norm spheres, and introduce a 
projected gamma family of distributions defined through the normalization a vector of 
independent gamma random variables to the $p$-norm sphere.  This family serves as a 
building block for a flexible family of distributions obtained as a Dirichlet process 
mixture of projected gammas.  For model assessment, we discuss scoring methods appropriate 
to distributions on the unit hypercube.  In particular, working with the energy score
criterion, we develop a kernel metric that produces a  proper scoring rule, and present 
a simulation study to compare  different modeling choices using the proposed scoring rules.  
Finally we apply our  approach to describe the dependence structure of the extreme values of 
the magnitude  of the integrated vapor transport (IVT), data describing the flow 
of atmospheric moisture along the coast of California for the years of 1979 
through 2020.  We find clear but heterogeneous geographical dependence.

### 2024-04-10 conclusion.tex
push for mdpi resubmission

Establishing the angular measure
    specifically in $\mathbb{S}_{\infty}^{d-1}$ provides two benefits over 
    $\mathbb{S}_p^{d-1}$.  First, the transformation to 
    $\mathbb{S}_{\infty}^{d-1}$ is unique.  Observe in 
    Equation~\eqref{eqn:pnormtinv}, establishing $y_d$ as a function
    of $y_1,\ldots,y_{d-1}$ can be replaced in form with any $y_{\ell}$, 
    indicating there are $d$ equivalent transformations, each yielding a different
    Jacobian and, for $p>1$, potentially resulting in a different calculated density.  
    Second, evaluation of geodesic distance on $\mathbb{S}_p^{d-1}$ is not 
    straightforward.  However, we have demonstrated a computationally efficient 
    upper bound on geodesic distance on $\mathbb{S}_{\infty}^{d-1}$.  Accepting
    these foibles, it would be interesting to explore the distribution on 
    $\mathbb{S}_{p}^{d-1}$,

%We explored the behavior of the proposed model using simulated data from
    %mixtures of projected Gammas with varying degrees of complexity---both 
    %in terms of dimensionality and in number of mixture components.  From this,
    %we observed that the additional flexibility offered by varying the $\beta$
    %term---the rate parameter of the gamma distribution---can offer additional
    %model fidelity.  \makenote{However,} this result is not borne out in our 
    %real data example, for which in higher dimensions the simpler model is 
    %strongly preferred.  Additionally, we observe
    %that the choice of the log-normal centering distribution and additional
    %flexibility it offers did not translate to additional model fidelity.  
    %\makenote{This result is borne out in the real data, where it performed at best 
    %comparably to the gamma model.}  
    % This
    % is borne out in the real data, where on the ERA--Interim dataset it performed
    % only comparably, but on ERA--5 it performed significantly worse.
    % {\bf I am not sure that this paragraph is appropriate anymore. I think that
    % the different mixture models considered are pretty much equivalent, so we should
    % favor the one that is easiest and most robust to fit.}

The computations in this paper were performed on a desktop computer with an 
    AMD Ryzen 5000 series processor. The program is largely single-threaded, so 
    computation time is not dependent on available core count.  In each case, 
    we run the MCMC chain for 50\,000 iterations, with a burn-in of 40\,000 
    samples.  Fitting the PG--G model on the ERA5 dataset took approximately 
    15 minutes.  Work is in progress to optimize the code, and explore 
    parallelization where possible.  We are also exploring alternative 
    computational approaches that will make it feasible to tackle very high 
    dimensional problems, such as variational Bayes. In fact, to elaborate on 
    the study of IVT, there is a need to consider several hundreds, if not thousands, 
    of grid cells over the Pacific Ocean in order to obtain a good description of 
    atmospheric events responsible for large storm activity over California.

>>>>

Developing an angular measure specifically in $\mathbb{S}_{\infty}^{d-1}$ provides 
    two benefits over $\mathbb{S}_p^{d-1}$.  First, the transformation to 
    $\mathbb{S}_{\infty}^{d-1}$ is unique.  Recall that 
    Equation~\eqref{eqn:pnormtinv} gives $y_d$ as a function
    of $y_1,\ldots,y_{d-1}$. An analogous expression can be obtained for
    any $y_{\ell}$. This indicates that there are $d$ equivalent transformations, 
    each yielding a different
    Jacobian and, for $p>1$, potentially resulting in a different density.  
    Second, evaluation of geodesic distances on $\mathbb{S}_p^{d-1}$ is not 
    straightforward.  However, we have demonstrated a computationally efficient 
    upper bound on geodesic distance on $\mathbb{S}_{\infty}^{d-1}$.  Accepting
    these foibles, it would be interesting to explore the distribution on 
    $\mathbb{S}_{p}^{d-1}$,

The computations in this paper were performed on a desktop computer with an 
    AMD Ryzen 5000 series processor. The program is largely single-threaded, so 
    computation time is not dependent on available core count.  In each case, 
    we run the MCMC chain for 50\,000 iterations, with a burn-in of 40\,000 
    samples.  Fitting the PG-G model on the ERA5 dataset took approximately 
    15 minutes.  Work is in progress to optimize the code, and explore 
    parallelization where possible.  We are also exploring alternative 
    computational approaches that will make it feasible to tackle very high 
    dimensional problems, such as variational Bayes. In fact, to elaborate on 
    the study of IVT, there is a need to consider several hundreds, if not thousands, 
    of grid cells over the Pacific Ocean in order to obtain a good description of 
    atmospheric events responsible for large storm activity over California.

### 2024-04-10 introduction.tex
entropy submission RC1
push for mdpi resubmission

During the last decade or so, much work has been done in the exploration of the 
    definition and properties of an appropriate generalization of the univariate 
    GP distribution to a multivariate setting.  To mention some of the papers on 
    the topic, the work of \citep{rootzen2006} defines the generalized Pareto 
    distribution, with further analysis on these classes of distributions 
    presented in \cite{falk2008} and \cite{michel2008}.  A recent review of the 
    state of the art in multivariate peaks over threshold modelling using 
    generalized Pareto is provided in \cite{rootzen2018} while \cite{RoSeWa2018a} 
    provides insight on the theoretical properties of possible parametrizations. 
    These are use in \cite{KiRoSeWa2019} for likelihood-based models for PoT 
    estimation. A frequently used method for describing the dependence in 
    multivariate distributions is to use a copula. \cite{renard2007}, and 
    \cite{falk2019} provide successful  examples of this approach in an EVT 
    framework. \cite{ferreira2014} presents a constructive definition of the 
    Pareto process, that generalizes the GP to an infinite dimensional setting. It 
    consists of decomposing the process into independent radial and angular 
    components. Such an approach can be used in the finite dimensional case, where 
    the angular component contains the information pertaining to the dependence 
    structure of the random vector. Based on this definition, we present a novel 
    approach for modelling  the angular component with families of distributions 
    that provide flexibility and can be applied in a moderately large dimensional 
    setting.  Our focus on the angular measure is similar to that in \cite{boldi2007},
    \cite{SaNa2014} and \cite{HaCaCh2017}, that consider Bayesian non-parametric 
    approaches. Yet, our approach differs in that it is established in the 
    peaks-over-threshold regime, and avoids the problem of dealing with the so 
    called moment constraint by considering a constructive definition of the 
    multivariate GP, based on the infinity norm. The approach proposed in this paper
    adds to the growing literature on Bayesian models for multivariate extreme
    value analysis (see, for example, \cite{boldi2007},\cite{guillotte2011},
    \cite{SaNa2014},\cite{hanson2017}), providing a model that has strong computational
    advantages due its structural simplicitly, achieves flexibility using 
    a mixture model, imposes no moment constraints, and scales well to moderately 
    large dimensions.

The remainder of this paper is outlined as follows. 
    Section~\ref{sec:multivariatepot} comprises a brief review of multivariate PoT, 
      detailing the separation of the radial measure from the angular measure.
    Section~\ref{sec:methodology} details our approach for estimating the angular 
      measure, based on projecting an arbitrary distribution supported in ${\mathbb R}_+^d$ 
      onto unit hyper-spheres defined by $p$-norms. 
    Section~\ref{sec:evaluation} develops criteria for model selection in the support 
      of the angular measure.  
    Section~\ref{sec:results} explores the efficacy of the proposed approach on a set 
      of simulated data, and, acknowledging the relevance of extreme value theory to 
      climatological events~\citep{jentsch2007,vousdoukas2018,li2019}, estimates the 
      extremal dependence structure for a measure of water vapor flow in the atmosphere, 
      used for identifying atmospheric rivers.  
    Finally, Section~\ref{sec:conclusion} presents our conclusions and discussion.

Throughout the paper, we adopt the operators $\wedge$ to denote minima, and 
    the $\vee$ to denote maxima.  Thus $\wedge_i s_i = \min_i s_i$, and 
    $\vee_i s_i = \max_i s_i$.  These operators can also be applied component-wise 
    between vectors, such as $\bm{a}\wedge\bm{b} = (a_1\wedge b_1, a_2\wedge b_2,\ldots)$.  
    We use uppercase to indicate random variables, lowercase to indicate points, and
    bold-face to indicate vectors or matrices thereof.

\section{A multivariate PoT model\label{sec:multivariatepot}}
To develop a multivariate PoT model for extreme values consider a 
    $d$-dimensional random vector $\bm{W} = (W_1, \ldots ,W_d)$ with
    cumulative distribution $F$. Following \cite{RoSeWa2018a}, assume 
    that there exists sequences of vectors $\bm{a}_n$ and $\bm{b}_n$,
    and a $d$-variate distribution $G$ such that 
    $\lim_{n\rightarrow\infty} F^n(\bm{a}_n \bm{w} + \bm{b}_n) = 
    G(\bm{w})$. $G$ is a $d$-variate generalized extreme value 
    distribution. It follows that
    \begin{equation*}
        \begin{aligned}
        \lim\limits_{n\rightarrow\infty} &\prob{\bm{a}^{-1}_n (\bm{W} - \bm{b}_n) 
      \leq \bm{w} \mid \bm{W} \not\leq \bm{b}_n)} \\ 
        &\hspace{0.5cm}= \frac{\log G(\bm{w} \wedge \bm{0}) 
        - \log G(\bm{w}) }{\log G(\bm{0})} = H(\bm{w}).
        \end{aligned}
    \end{equation*}
    $H$ is a multivariate Pareto distribution, and corresponds to a joint
    distribution conditional on exceeding a multivariate threshold. In addition to
    a copula function, $H$ depends on two $d$-dimensional vectors of 
    parameters that we denote as $\bm{\xi}$ for the shapes and $\bm{\sigma}$ 
    for the scales. \cite{RoSeWa2018a} provide a number of stochastic 
    representations for $H$.  In particular, denote as $Z$ a
    random variable with distribution $H$ where $\bm{\xi}= 1$ and 
    $\bm{\sigma} = 0$.  Then, Remark 1 justifies the representation in 
    \cite{ferreira2014}, giving $\bm{Z} = \bm{V}R$
    where $R$ and $\bm{V}$ are independent. $R = \|\bm{Z}\|_\infty$ is 
    distributed as a standard Pareto random variable, and $\bm{V} = 
    \bm{Z}/\|\bm{Z}\|_\infty$ is a random vector in  
    $\mathbb{S}_{\infty}^{d-1}$, the positive orthant of the 
    unit sphere under $\mathcal{L}_{\infty}$ norm, with distribution $\Phi$. 
    This representation is central to the methods proposed in this paper.
    $R$ and $\bm{V}$ are referred to, respectively, as the {\em radial} 
    and {\em angular} components of $H$. The angular measure controls 
    the dependence  structure of $\bm{Z}$  in the tails. In view of 
    this, to obtain a  PoT model we seek a flexible model for the 
    distribution of $\bm{V} \in {\mathbb S}_{\infty}^{d-1}$.

The approach considered in \cite{rootzen2018} focuses on the limiting
    conditional distribution $H$. An alternative approach consists of assuming
    that regular variation \cite[see, for example,][]{resnick2008extreme} holds 
    for the limiting distribution of $\bm{W}$, implying
    \[
        \lim\limits_{n\rightarrow\infty} n \prob{n^{-1} \bm{W}\in A} = 
        \mu(A),
    \]
    where $\mu$ is termed the exponent measure. $\mu$ has the homogeneity property
    $\mu(tA) = t^{-1}\mu(A)$. Letting $\rho = \|W\|_p, p>0$ 
    and $\bm{\theta} = \bm{W}/\rho$, define  $\Psi(B) = \mu(\{\bm{w} : \rho>1, 
    \bm{\theta} \in B\})$, which is referred to as the angular measure. After 
    some manipulations, we obtain that
    \begin{equation}
    \label{exponent-mu}
        \lim\limits_{r\rightarrow\infty} 
        \text{Pr}\left[\bm{\theta}\in A \rvert \rho>r\right] = 
            \frac{\Psi(A)}{\Psi({\mathbb S}_p^{d-1})} .
    \end{equation}
    Thus, a model for the exponent measure induces a model for the limiting distribution
    conditional on the observations being above a threshold defined with respect
    to their $p$-norm. The constraint that all marginals of $\mu$ correspond to a
    standard Pareto distribution leads to the so called moment constraints on $\Psi$. 
    Inference for the limiting distribution of the exceedances
    needs to account for the normalizing constant in Equation (\ref{exponent-mu}), as well
    the moment constraints. In addition, the moment constraints can impose unrealistic
    symmetries in the data distribution.

>>>>

During the last decade or so, much work has been done in the exploration of the 
    definition and properties of an appropriate generalization of the univariate 
    GP distribution to a multivariate setting.  To mention some of the papers on 
    the topic, the work of \citep{rootzen2006} defines the generalized Pareto 
    distribution, with further analysis on these classes of distributions 
    presented in \cite{falk2008} and \cite{michel2008}.  A recent review of the 
    state of the art in multivariate peaks over threshold modelling using 
    generalized Pareto is provided in \cite{rootzen2018} while \cite{RoSeWa2018a} 
    provides insight on the theoretical properties of possible parametrizations. 
    These are used in \cite{KiRoSeWa2019} for likelihood-based models for PoT 
    estimation. A frequently used method for describing the dependence in 
    multivariate distributions is to use a copula. \cite{renard2007}, and 
    \cite{falk2019} provide successful examples of this approach in an EVT 
    framework.

    \cite{ferreira2014} presents a constructive definition of the 
    Pareto process, that generalizes the GP to an infinite dimensional setting. It 
    consists of decomposing the process into independent radial and angular 
    components. Such an approach can be used in the finite dimensional case, where 
    the angular component contains the information pertaining to the dependence 
    structure of the random vector. Based on this definition, we present a novel 
    approach for modelling  the angular component with families of distributions 
    that provide flexibility and can be applied in a moderately large dimensional 
    setting.  Our focus on the angular measure is similar to that in \cite{boldi2007},
    \cite{SaNa2014} and \cite{HaCaCh2017}, that consider Bayesian non-parametric 
    approaches. Yet, our approach differs in that it is established in the 
    peaks-over-threshold regime, and uses a constructive definition of the 
    multivariate GP, based on the infinity norm. The approach proposed in this paper
    adds to the growing literature on Bayesian models for multivariate extreme
    value analysis (see, for example, \cite{boldi2007},\cite{guillotte2011},
    \cite{SaNa2014},\cite{hanson2017}), providing a model that has strong computational
    advantages due its structural simplicitly, achieves flexibility using 
    a mixture model, and scales well to moderately large dimensions.

The remainder of this paper is outlined as follows. 
    Section~\ref{sec:multivariatepot} comprises a brief review of multivariate PoT, 
      detailing the separation of the radial measure from the angular measure.
    Section~\ref{sec:methodology} details our approach for estimating the angular 
      measure, based on transforming an arbitrary 
      distribution supported in ${\mathbb R}_+^d$ 
      onto unit hyper-spheres defined by $p$-norms. 
    Section~\ref{sec:evaluation} develops criteria for model selection in the support 
      of the angular measure.  
    Section~\ref{sec:results} explores the efficacy of the proposed approach on a set 
      of simulated data, and, acknowledging the relevance of extreme value theory to 
      climatological events~\citep{jentsch2007,vousdoukas2018,li2019}, estimates the 
      extremal dependence structure for a measure of water vapor flow in the atmosphere, 
      used for identifying atmospheric rivers.  
    Finally, Section~\ref{sec:conclusion} presents our conclusions and discussion.

Throughout the paper, we adopt the operators $\wedge$ to denote minima, and 
    the $\vee$ to denote maxima.  Thus $\wedge_i s_i = \min_i s_i$, and 
    $\vee_i s_i = \max_i s_i$.  These operators can also be applied component-wise 
    between vectors, such as $\bm{a}\wedge\bm{b} = (a_1\wedge b_1, a_2\wedge b_2,\ldots)$.  
    Similarly, we apply inequality and arithmetic operators operators to vectors, for
    example $\bm{a}\leq \bm{b}$, and interpret them component-wise.
    We use uppercase to indicate random variables, lowercase to indicate points, and
    bold-face to indicate vectors or matrices thereof.

\section{A multivariate PoT model\label{sec:multivariatepot}}
To develop a multivariate PoT model for extreme values consider a 
    $d$-dimensional random vector $\bm{W} = (W_1, \ldots ,W_d)$ with
    cumulative distribution $F$. A common assumption on 
    $\bm{W}$ is that it is in the so called domain of attraction of 
    a multivariate max-stable distribution, $G$. Thus, following \cite{RoSeWa2018a}, assume 
    that there exists sequences of vectors $\bm{a}_n$ and $\bm{b}_n$,
    such that $\lim_{n\rightarrow\infty} F^n(\bm{a}_n \bm{w} + \bm{b}_n) = 
    G(\bm{w})$. $G$ is a $d$-variate generalized extreme value 
    distribution. Notice that, even though the univariate marginals are obtained from 
    a three parameter family, there is no parametric form to represent $G$.
    Taking logarithms and expanding, we have that 
    \[  
        \lim\limits_{n\rightarrow\infty} n(1 - F(\bm{a}_n \bm{w} + \bm{b}_n)) = 
        -\log G(\bm{w}), 
    \]
    $\forall \bm{w\in{\mathbb R}^d}$ such that $G(\bm{w})>0$. It follows that
    \begin{multline*}
        \lim\limits_{n\rightarrow\infty} \prob{\bm{a}^{-1}_n (\bm{W} - \bm{b}_n) 
      \leq \bm{w} \mid \bm{W} \not\leq \bm{b}_n)} = 
         \frac{\log G(\bm{w} \wedge \bm{0}) 
        - \log G(\bm{w}) }{\log G(\bm{0})} = H(\bm{w}),
    \end{multline*}
    where $\bm{a}_n^{-1}$ indicates element-wise inversion, and 
    $\{\bm{W} \not\leq \bm{b}_n\}$ denotes the set where at least one coordinate is above 
    the corresponding  component of $\bm{b}_n$.  
    $H$ is a multivariate Pareto distribution.  It corresponds to a joint
    distribution conditional on exceeding a multivariate threshold. $H$
    is defined by a non-parametric function governing the multivariate dependence, and 
    two $d$-dimensional vectors of 
    parameters that control the shapes and scales of the
    marginals. We denote these as $\bm{\xi}$ for the shapes and $\bm{\sigma}$ 
    for the scales.  \cite{RoSeWa2018a} provides a number of stochastic 
    representations for $H$.  In this paper we focus in a
    particular one that is proposed in \cite{ferreira2014}. To this end, 
    we denote as $Z$ a random variable with distribution $H$ where $\bm{\xi}= 1$ 
    and $\bm{\sigma} = 0$.  Then, $\bm{Z} = R\bm{V}$ where $R$ and $\bm{V}$ 
    are independent. $R = \|\bm{Z}\|_\infty= \vee_{i=1}^d Z_i$ is
    distributed as a standard Pareto random variable, and 
    $\bm{V} = \bm{Z}/\|\bm{Z}\|_\infty$ is a random vector in  
    $\mathbb{S}_{\infty}^{d-1}$, the positive orthant of the 
    unit sphere under $\mathcal{L}_{\infty}$ norm, with distribution $\Phi$. 
    This representation is central to the methods proposed in this paper.
    $R$ and $\bm{V}$ are referred to, respectively, as the {\em radial} 
    and {\em angular} components of $H$. The angular measure controls 
    the dependence  structure of $\bm{Z}$  in the tails. In view of 
    this, to obtain a  PoT model we seek a flexible model for the 
    distribution of $\bm{V} \in {\mathbb S}_{\infty}^{d-1}$, based
    on a Bayesian non-parametric model.

The approach considered in \cite{rootzen2018} focuses on the limiting
    conditional distribution $H$. An alternative approach to obtaining a limiting 
    PoT distribution consists of assuming
    that regular variation \cite[see, for example,][]{resnick2008extreme} holds 
    for the limiting distribution of $\bm{W}$, implying that
    \[
        \lim\limits_{n\rightarrow\infty} n \prob{n^{-1} \bm{W}\in A} = 
        \mu(A),
    \]
    for some measure $\mu$ that is referred to as the exponent measure. 
    $\mu$ has the homogeneity property $\mu(tA) = t^{-1}\mu(A)$. 
    Letting $\rho = \|W\|_p, p>0$ 
    and $\bm{\theta} = \bm{W}/\rho$, define  $\Psi(B) = \mu(\{\bm{w} : \rho>1, 
    \bm{\theta} \in B\})$, which is referred to as the angular measure. After 
    some manipulations, we obtain that
    \begin{equation}
    \label{exponent-mu}
        \lim\limits_{r\rightarrow\infty} 
        \text{Pr}\left[\bm{\theta}\in A \rvert \rho>r\right] = 
            \frac{\Psi(A)}{\Psi({\mathbb S}_p^{d-1})} .
    \end{equation}
    Thus, a model for the exponent measure induces a model for the limiting distribution
    conditional on the observations being above a threshold defined with respect
    to their $p$-norm. The constraint that all marginals of $\mu$ correspond to a
    standard Pareto distribution leads to the so called moment constraints on $\Psi$, consisting
    of
    \[
    \int_{{\mathbb S}_p^{d-1}} w_i \,d\Psi(\bm{w}) = \frac{1}{d}, \;\; i=1, \ldots , d.
    \]
    Inference for the limiting distribution of the exceedances
    needs to account for the normalizing constant in Equation~\eqref{exponent-mu}, as well
    the moment constraints. Because of these issues, in this paper
    we prefer to follow the limiting conditional distribution approach. An example of 
    the application of the regular variation approach, using $p=1$ is developed in \cite{SaNa2014}.

### 2024-04-10 main.tex
push for mdpi resubmission

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
%=================================================================
\documentclass[entropy,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2024}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates
%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{subcaption}
\captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=6pt, 
        belowskip=6pt,
        singlelinecheck=off,
        justification=justified}   
%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
\newtheorem{prop}{Proposition}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\bigmid}{\,\middle\vert\,}
\newcommand{\bruno}[1]{\textcolor{red}{#1}} % Bruno edits - red
\newcommand{\makenote}[1]{\textcolor{teal}{#1}} % Peter edits - teal
\newcommand{\findcite}{\textcolor{red}{[Find Citation]}}
\newcommand{\needcite}{\findcite}
\newcommand{\Chi}{\mbox{\Large$\chi$}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\inorm}[1]{\norm{#1}_{\infty}}
\newcommand{\pnorm}[2]{\norm{#1}_{#2}}
\newcommand{\prob}[1]{\text{Pr}\left[#1\right]}
\newcommand{\expect}[1]{\text{E}\left[#1\right]}
%=================================================================
% Full title of the paper (Capitalized)
\Title{Bayesian non-parametric inference for multivariate peaks-over-threshold models}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
% \abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
\abstract{We consider a constructive definition of the multivariate Pareto that factorizes the 
random vector into a radial component and an independent angular component; The former
following a univariate Pareto distribution, and the latter defined on the surface of the 
positive orthant of the infinity norm unit hypercube.   We propose a method 
for inferring the distribution of the angular component, by identifying its support 
as the limit of the positive orthant of the unit $p$--norm spheres, and introduce a 
projected gamma family of distributions defined through the normalization of a vector of 
independent random gammas to the space.   This serves in constructing a flexible family of
distributions obtained as a Dirichlet process mixture of projected gammas.  For model 
assessment, we discuss scoring methods appropriate to distributions on the unit hypercube.  
In particular, working with the energy score criterion, we develop a kernel metric that 
produces a proper scoring rule, and present 
a simulation study to compare different modeling choices using the proposed metric.    
Using our approach, we describe the dependence structure of extreme values in the
integrated vapor transport (IVT), data describing the flow of atmospheric moisture 
along the coast of California.  We find clear but heterogeneous geographical dependence.}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
%=================================================================
\documentclass[entropy,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2024}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates
%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{subcaption}
\captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=6pt, 
        belowskip=6pt,
        singlelinecheck=off,
        justification=justified}   
%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
\newtheorem{prop}{Proposition}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\bigmid}{\,\middle\vert\,}
\newcommand{\bruno}[1]{\textcolor{red}{#1}} % Bruno edits - red
\newcommand{\makenote}[1]{\textcol:or{teal}{#1}} % Peter edits - teal
\newcommand{\findcite}{\textcolor{red}{[Find Citation]}}
\newcommand{\needcite}{\findcite}
\newcommand{\Chi}{\mbox{\Large$\chi$}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\inorm}[1]{\norm{#1}_{\infty}}
\newcommand{\pnorm}[2]{\norm{#1}_{#2}}
\newcommand{\prob}[1]{\text{Pr}\left[#1\right]}
\newcommand{\expect}[1]{\text{E}\left[#1\right]}
%=================================================================
% Full title of the paper (Capitalized)
\Title{Bayesian non-parametric inference for multivariate peaks-over-threshold models}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
% \abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
\abstract{We consider a constructive definition of the multivariate Pareto that factorizes the 
random vector into a radial component and an independent angular component; The former
following a univariate Pareto distribution, and the latter defined on the surface of the 
positive orthant of the infinity norm unit hypercube.   We propose a method 
for inferring the distribution of the angular component, by identifying its support 
as the limit of the positive orthant of the unit $p$-norm spheres, and introduce a 
projected gamma family of distributions defined through the normalization of a vector of 
independent random gammas to the space.   This serves in constructing a flexible family of
distributions obtained as a Dirichlet process mixture of projected gammas.  For model 
assessment, we discuss scoring methods appropriate to distributions on the unit hypercube.  
In particular, working with the energy score criterion, we develop a kernel metric that 
produces a proper scoring rule, and present 
a simulation study to compare different modeling choices using the proposed metric.    
Using our approach, we describe the dependence structure of extreme values in the
integrated vapor transport (IVT), data describing the flow of atmospheric moisture 
along the coast of California.  We find clear but heterogeneous geographical dependence.}
